%
% Regulatory.tex
%
% LulzBot® Mini User Manual
%
% Copyright (C) 2014 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%




\section{\texttt{Regulatory Compliance Statement Class B}}

\subsection{\texttt{Federal Communications Commission Statement}}
\index{FCC}

This device complies with part 15 class B of the FCC Rules. Operation is
subject to the following two conditions:
\begin{enumerate}
\item This device may not cause harmful interference and
\item This device must accept any interference received, including interfer-
ence that may cause undesired operation.
\end{enumerate}


\texttt{NOTE:} This equipment has been tested and found to comply with the
limits for a Class B digital device, pursuant to part 15 of the FCC Rules.
These limits are designed to provide reasonable protection against harmful
interference in a residential installation. This equipment generates, uses
and can radiate radio frequency energy and, if not installed and used in
accordance with the instructions, may cause harmful interference to radio
communications. However, there is no guarantee that interference will not
occur in a particular installation. If this equipment does cause harmful
interference to radio or television reception, which can be determined by
turning the equipment off and on, the user is encouraged to try to correct
the interference by one or more of the following measures:
\begin{enumerate}
\item Reorient or relocate the receiving antenna.
\item Increase the separation between the equipment and receiver.
\item Connect the equipment into an outlet on a circuit different from that
to which the receiver is connected.
\item Consult the dealer or an experienced radio/TV technician for help.
\end{enumerate}

\textcolor{red}{FCC Warning:}
\textcolor{red}{Changes or modifications not approved by the party responsible for compliance could void the users authority to operate the equipment.}


\subsection{\texttt{Industry Canada Statement}}
\index{ICES}
CAN ICES-3 (B)/NMB-3(B)
Cet appareil numérique de la classe B est conforme à la norme ICES-003
du Canada. This device complies with Canadian ICES-003 Class B.

\subsection{\texttt{Australian Communications and Media Authority Statement}}
\index{Australia}
\index{New Zealand}
This device has been tested and found to comply with the limits for a
Class B digital device, pursuant to the Australian/New Zealand standard AS/NZS CISPR 22:2009 + A1:2010.
