%
% Warnings.tex
%
% LulzBot® Mini User Manual
%
% Copyright (C) 2014 Aleph Objects, Inc.
%
% This document is licensed under the Creative Commons Attribution 4.0
% International Public License (CC BY-SA 4.0) by Aleph Objects, Inc.
%

\section{\texttt{Read Me First!}}
\index{warnings}
\index{hazards}
\textcolor{red}{READ THIS MANUAL COMPLETELY BEFORE UNPACKING AND POWERING UP YOUR PRINTER.}

\section{\texttt{Hazards and Warnings}}

Your LulzBot Mini 3D printer has motorized and heated parts.  Always be aware of possible hazards when the printer is operational.


\subsection{\textcolor{red}{Electric Shock Hazard}}
\index{electronics}
\index{wires}
\index{power supply}
Never open the electronics case when the printer is powered on. Before removing the electronics case cover, always power down the printer and completely turn off and unplug the printer. Allow the printer to discharge for at least one minute.

\subsection{\textcolor{red}{Burn Hazard}}
\index{extruder}
\index{heater block}
\index{temperature}
\index{burns}
Never touch the hot end nozzle or heater block without first turning off the hot end and allowing it to completely cool down. The hot end can take up to 20 minutes to completely cool. Never touch recently extruded plastic. The plastic can stick to your skin and cause burns. The print surface can reach high temperatures that are capable of causing burns.

\subsection{\textcolor{red}{Fire Hazard}}
Never place flammable materials or liquids on or near the printer when it is powered on or operational. Liquid acetone, alcohol, or other chemicals may release vapors that are extremely flammable.

\subsection{\textcolor{red}{Pinch Hazard}}

When the printer is operational take care to never put your fingers near any moving parts including belts, pulleys, or gears. Tie back long hair or clothing that can get caught in the moving parts of the printer.

\subsection{\textcolor{red}{Age Warning}}

For users under the age of 18, adult supervision is recommended. Beware of choking hazards around small children.

%\subsection{\textcolor{red}{Modifications and Repairs Warning}}

%At Aleph Objects, Inc. we respect your freedom to modify your LulzBot\textsuperscript{\miniscule{\textregistered}} desktop 3D printer. However any modifications or attempted repairs that cause damage are not covered under the Warranty. Questions? Contact Technical Support by emailing \texttt{support@lulzbot.com}, or by calling +1-970-377-1111.


\subsection{\textcolor{red}{Modifications and Repairs Warning}}

At Aleph Objects, Inc., we respect your freedom to modify your LulzBot desktop 3D printer. However any modifications or attempted repairs that cause damage are not covered under the Warranty. Questions? Contact Technical Support by emailing \texttt{support@lulzbot.com}, or by calling +1-970-377-1111.

